Automated discovery of interpretable gravitational-wave population models

### 2022-07-11 src/tex/ms.tex
Give definitions of complexity

Internal to \pysr, a multi-objective optimization problem is solved: the evolution seeks to find expressions which are as accurate as possible, while being as simple as possible.
Formally, for our setting, \pysr solves the following optimization problem:
\begin{align}
    s_c &= 
        \mathop{\arg\min}_{
            \tiny
            \begin{array}{c}s\in\mathcal{S}\\ \abs{s} = c \end{array}
        }
        \mathcal{L}(s),
    \quad\text{for each } c\in \mathcal{C},\nonumber\\
    &\text{where }\mathcal{L}(s) = \sum_i \ell(s(\mathbf{x}_i), y_i)
\end{align}
where $s$ is an expression, 
$\mathcal{S}$ is a space of possible expressions considered,
$\abs{s}$ is the complexity of an expression $s$,
$\ell$ is the loss function, and $\{(x_i, y_i)\}$ is the dataset
for $x_i$ each input and $y_i$ the label.
The most accurate expression at each $c$, denoted as $s_c$, is computed for a given set range of $c$, which we choose as $c\in\mathcal{C}\equiv \{1, \ldots, 50\}$.
Complexity is defined here
as a sum of the complexity of each symbol in the expression,
and $\ell(\hat{y}_i, y_i) = \qty(\hat{y}_i - y_i)^2$.
% \todo{What complexities were chosen?}

>>>>

Internal to \pysr, a multi-objective optimization problem is solved: the evolution seeks to find expressions which are as accurate as possible, while being as simple as possible.
Formally, for our setting, \pysr solves the following optimization problem:
\begin{align}
    s_c &= 
        \mathop{\arg\min}_{
            \tiny
            \begin{array}{c}s\in\mathcal{S}\\ \abs{s} = c \end{array}
        }
        \mathcal{L}(s),
    \quad\text{for each } c\in \mathcal{C},\nonumber\\
    &\text{where }\mathcal{L}(s) = \sum_i \ell(s(\mathbf{x}_i), y_i)
\end{align}
where $s$ is an expression, 
$\mathcal{S}$ is a space of possible expressions considered,
$\abs{s}$ is the complexity of an expression $s$,
$\ell$ is the loss function, and $\{(x_i, y_i)\}$ is the dataset
for $x_i$ each input and $y_i$ the label.
The most accurate expression at each $c$, denoted as $s_c$, is computed for a given set range of $c$, which we choose as $c\in\mathcal{C}\equiv \{1, \ldots, 50\}$.
Complexity is defined here
as the number of symbols in the expression (including repeats),
and $\ell$ is defined as $(\hat{y}_i, y_i) = \qty(\hat{y}_i - y_i)^2$.
